Draft_markdown_v1

### 2024-04-09 Draft_V1.Rmd
Update Draft_V1.Rmd

# lower case text with keywords
tidy_data_notoken <- data %>%
  mutate(desc = tolower(text)) %>%
  filter(grepl(all_words, desc))
```

@@

filtered_ratio_count$Year <- as.numeric(as.character(filtered_ratio_count$Year))
```

@@

```{r}
url <- "https://github.com/RiverKim-garam/CTA24-Final-assessment/blob/main/local_glove.rds?raw=true"
golve_embedding <- readRDS(url(url, method = "libcurl"))
```

@@

# Add the labels of the words to the dataframe
df_glove_umap$word <- rownames(df_glove_umap)
colnames(df_glove_umap) <- c("UMAP1", "UMAP2", "word")
```

>>>>

# lower case text with keywords
tidy_data_notoken <- data %>%
  mutate(desc = tolower(text)) %>%
  filter(grepl(all_words, desc))

tidy_data_notoken %>%
  group_by(party) %>%
  summarise(count = n()) %>%
  arrange(desc(count))
```

@@

filtered_ratio_count$Year <- as.numeric(as.character(filtered_ratio_count$Year))

```

@@

```{r}
url <- "https://github.com/RiverKim-garam/CTA24-Final-assessment/blob/main/local_glove.rds?raw=true"
glove_embedding <- readRDS(url(url, method = "libcurl"))
```

@@

# Add the labels of the words to the dataframe
df_glove_umap$word <- rownames(df_glove_umap)
colnames(df_glove_umap) <- c("UMAP1", "UMAP2", "word")

```
